\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Doodle Classification}

\author{
	\IEEEauthorblockN{He, Jingyi}
	260------ \\
	Kaggle Team: Bernoudles \\
	\IEEEauthorblockA{email address}
	\and
	\IEEEauthorblockN{Rahman, Aanika}
	260662187 \\
	Kaggle Team: Bernoudles \\
	\IEEEauthorblockA{aanika.rahman@mail.mcgill.ca}
	\and
	\IEEEauthorblockN{Zhao, Zhuoran}
	260------ \\
	Kaggle Team: Bernoudles \\
	\IEEEauthorblockA{email address}
}

\maketitle

\section{Introduction} 
\emph{Briefly describe the problem and summarize your approach and results.}
\\
\\

\section{Feature Design} 
\emph{Describe and justify your pre-processing methods, and how you designed and selected your features.}
\\
\\

\section{Algorithms}
\emph{Give an overview of the learning algorithms used without going into too much detail in the class notes (e.g. SVM derivation, etc.), unless necessary to understand other details.}
\\
\\

\section{Methodology}
\emph{Include any decisions about training/validation split, distribution choice for naive bayes, regularization strategy, any optimization tricks, setting hyper-parameters, etc.}
\\
\\

\section{Results}
\emph{Present a detailed analysis of your results, including graphs and tables as appropriate. This analysis should be broader than just the Kaggle result: include a short comparison of the most important hyperparameters and all 3 methods you implemented.}
\\
\\

\section{Discussion} 
\emph{Discuss the pros/cons of your approach \& methodology and suggest areas of future work.}
\\
\\

\section{Statement of Contributions} \emph{Briefly describe the contributions of each team member towards each of the components of the project (e.g. defining the problem, developing the methodology, coding the solution, performing the data analysis, writing the report, etc.)}
\\
\\ The authors, Jingyi He, Aanika Rahman and Zhuoran Zhao, have all taken direct roles in the all classifier implementations, methodology and model evaluations, feature preprocessing, as well as the composition of the report. 
\\
\\ We hereby state that all the work presented in this report is that of the authors.
\\
\\

\section*{Appendix (optional)} 
\emph{Here you can include additional results, more detail of the methods, etc.}
\\
\\

\bibliographystyle{plain}
\bibliography{report}

\end{document}